\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Khimraj Suthar}} & Email: \href{mailto:}{khimrajsuthar@gmail.com}\\
  \href{https://www.linkedin.com/in/khimraj-suthar-20b7aa122/}{LinkedIn: linkedin.com/in/khimraj-suthar-20b7aa122} & Mobile:~~~+91-8290285519 \\
  \href{https://github.com/khimraj}{Github: ~~github.com/khimraj} & \href{https://khimrajsuthar.com}{Website: ~~khimrajsuthar.com}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\vspace{-3pt}
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading{\href{https://webb.ai/}{Webb.ai }}{Remote}
    {Software Engineer, LLM}{January 2024 - Present}
    \begin{itemize}[label=$\circ$]
        \item Focusing on advancing the automation of troubleshooting processes for DevOps/SRE issues in cloud environments, leveraging expertise in deploying and optimizing LLM agents.
      \end{itemize}
\vspace{-4pt}
    \resumeSubheading{\href{https://www.ivy.homes/}{Ivy Homes }}{Bengaluru, IN}
    {Software Engineer, Machine Learning}{June 2021 - November 2023}
    \begin{itemize}[label=$\circ$]
        \item Steered the development of OCR, Entity Extraction, Document Classification, Text Clustering, Pricing(Valuation) Model, Liquidity Model, and intuitive Chatbot for real estate using ChatGPT.
\vspace{-3pt}
         \item Implemented Django-based Pricing Model with VPN security for safeguarding sensitive internal data.
      \end{itemize}
\vspace{-4pt}
    \resumeSubheading
		{\href{https://skillbee.com/}{Skillbee }}{Remote}
		{Machine Learning Intern}{April 2021 – June 2021}
		\begin{itemize}[label=$\circ$]
         \item Developed solutions for Job Recommendation and Relevance challenges.
\vspace{-3pt}
         \item Enhanced CV relevance on the platform from 65\% to 93\% through deep learning-based document classification.
       \end{itemize}
\vspace{-4pt}
    \resumeSubheading
		{\href{https://www.amazon.in/}{Amazon }}{Remote}
		{Software Development Engineer Intern}{May 2020 – July 2020}
		\begin{itemize}[label=$\circ$]
        \item Designed, developed, and deployed a responsive lender runbook website for Amazon Pay Later Service on AWS, reducing standard partner materials’ preparation and exchange time by 80\%.
\vspace{-3pt}
        \item Won a 3-day hackathon with 30+ participants, and secured a full-time job offer.
		\end{itemize}
\resumeSubHeadingListEnd

%-----------SKILL SUMMERY-----------------	    
\vspace{-3pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Proficient}{~~Python $|$ SQL $|$ Algorithms $|$ Data Science $|$ EDA $|$ AI $|$ Machine Learning $|$ Deep Learning $|$ NLP $|$ Generative AI $|$ LLM $|$ LangChain $|$ RAG $|$  Computer Vision $|$ AWS $|$ GCP $|$ Tenserﬂow $|$ Keras $|$ Scikit-Learn $|$ Numpy $|$ Pandas $|$ Matplotlib}
	\resumeSubItem{Familiar}{~~C $|$ C++ $|$ HTML $|$ CSS $|$ Java $|$ JavaScript $|$ Bootstrap $|$ JQuery $|$ GitHub $|$ Information Retrieval  $|$ CI/CD}
	\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\vspace{-3pt}
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{Paper: \href{https://ieeexplore.ieee.org/document/9117456}{Human Activity Recognition using Accelerometer and Gyroscope Data from Smartphones }}{Khimraj, P. K. Shukla, A. Vijayvargiya and R. Kumar, ”Human Activity Recognition using Accelerometer and Gyroscope Data from Smartphones” 2020 International Conference on Emerging Trends in Communication, Control and Computing (ICONC3), India, 2020.}
\vspace{2pt}
\resumeSubItem{Paper: \href{https://link.springer.com/article/10.1007/s13246-021-01071-6}{Voting-based 1D CNN model for human lower limb activity recognition using sEMG signal }}{Vijayvargiya A, Khimraj, Kumar R, Dey N. Voting-based 1D CNN model for human lower limb activity recognition using sEMG signal. Phys Eng Sci Med. 2021 Nov 8. doi: 10.1007/s13246-021-01071-6. Epub ahead of print. PMID: 34748192.}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-3pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{LLM Multi-Agent based Stock Selection and Price Prediction Model}{}
\vspace{-2pt}
\begin{itemize}[label=$\circ$]
\item Developed a model for the India and US markets with daily, weekly, and monthly stock price predictions, including prediction confidence scores.
\vspace{-3pt}
\item Utilized fundamental, historical price, and news data to aim for outperforming market index performance.
\end{itemize}
\vspace{-8pt}
\resumeSubItem{Indoor Localization For 5g And Beyond(BTech Thesis Group Project)}{}
\vspace{-2pt}
\begin{itemize}[label=$\circ$]
\item Pioneered a groundbreaking MOIL deep learning method for indoor localization through CSI data analysis.
\vspace{-3pt}
\item Achieved remarkable localization accuracy with mean distance errors of just 0.01m in Line-of-Sight (LOS) and 0.02m in Non-Line-of-Sight (NLOS) scenarios, surpassing existing techniques by an impressive 96\%.
\end{itemize}
\vspace{-8pt}
\resumeSubItem{Automated Tweets Report}{}
\vspace{-2pt}
\begin{itemize}[label=$\circ$]
\item Developed a Python script for keyword-based tweet collection, sentiment analysis, and Excel report generation.
\vspace{-3pt}
\item Deployed the solution on AWS EC2 for daily scheduled executions with automatic email delivery using cron jobs.
\end{itemize}
\vspace{-2pt}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Malaviya National Institute of Technology (MNIT)}{Jaipur, India}
      {Bachelor of Technology - Computer Science and Engineering;  CGPA: 7.70/10}{August 2017 - June 2021}
    \resumeSubHeadingListEnd
	
%-----------COURSEWORK-----------------	    
\vspace{-3pt}
\section{Coursework}
	\resumeSubHeadingListStart
	\resumeSubItem{Undergraduate}{~~Design and Analysis of Algorithms $|$ Data Structures and Algorithms $|$ Database Management System$|$ Operating System $|$ Computer Networks $|$ Digital Image Processing $|$ Natural Language Processing $|$ Object-Oriented Analysis and Design $|$ Deep Learning $|$ Advanced Topics in Databases $|$ Concurrent and Parallel Programming $|$ Software Engineering $|$ Computer Organization and Microprocessors $|$ Computer Architecture $|$ Compiler Design $|$ Systems Programming}
	\resumeSubItem{Additional}{~~Machine Learning $|$ Mathematics for ML $|$ Deep Learning Specialization $|$ TensorFlow Specialization $|$ Machine Learning in Production $|$ Generative AI with Large Language Models $|$ Trading Basics $|$ Trading Algorithms $|$ Advanced Trading Algorithms $|$ Creating a Portfolio $|$ Machine Learning for Trading Specialization} 
	\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\vspace{-3pt}
\section{Achievement}
\begin{description}[font=$\bullet$]
\item {Rated 1993 on \href{https://www.codechef.com/users/khimrajsuthar}{Codechef} and 1766 on \href{https://leetcode.com/khimrajsuthar/}{LeetCode}(Solved 500 problems).}
\vspace{-5pt}
\item {Secured 582/4700 rank in Round F and 608/6200 rank in Round H of Google Kick Start coding competition 2020.}

\end{description}

\end{document}
